\Large \bf Cyclone: Warp Speed Replication for Key Value Stores

### 2017-03-03 paper/paper.tex
bring back author names for circulation.
Switch to sigplanconf format.

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes,graphicx,url}
\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Cyclone: Replication Middleware for NVM Applications}

%for single author (just remove % characters)
%\author{
%  {\rm Paper #: XXX }\\
%  XXX
%  \and
%  {\rm YYY}\\
%  YYY
%} % end author

@@

\subsection*{Abstract}
The introduction of non-volatile directly attached memory in datacenters - in
the form of NVDIMMs and new memory technologies allows efficient data structures
to be built on non-volatile heaps that provide good performance coupled with
durability. However high availability remains a problem for these primarily
single machine solutions. While transactional interfaces built over RDMA capable
networking hardware offer a viable alternative, such hardware is often
unavailable in datacenters. Cyclone offers a solution to this problem by
providing transparent replication middleware that can be used with Intel's Non
Volatile Memory Library (NVML) to construct durable data-structures that map
keys to values.  Cyclone is designed around an optimized userspace networking
stack to reduce latency. Further, it can scale its consensus protocol across
cores and network ports to provide good throughput under load. We show that
Cyclone can replicate as many as 7 million updates a second using just 8 cores
(for the consensus protocol) and 4 commodity 10 GigE ports on each replica.

@@

\section{Conclusion}
Cyclone allows developers to add availability to key value maps built on top of
libraries such as NVML and achieve good performance on commodity networking
hardware. A key question is whether Cyclone can be used for other applications
such as filesystems? \emph{We believe that the requirement for scaling across
  multiple replication quorums can be satisfied by applications where the
  scalable commutativity rule~\cite{scalable_commutativity} applies to common
  case primitives.} Although our intitial release of Cyclone will be for key
value style applications, our on-going research is based on the scalable
commutativity hypothesis.
\newcommand\myurl[2]{\url{#1}}
\bibliographystyle{acm}
\bibliography{paper}

>>>>

\documentclass[10pt, preprint]{sigplanconf}
\usepackage{times,epsfig,endnotes,graphicx}
\usepackage{datetime, url, hyperref}

\conferenceinfo{SOSP'17}{October 29--31, 2017, Shanghai, China}
\copyrightyear{2017}

% These only appear when the 'preprint' option is specified.
% Enabling these will cause the first page of the document to fail the 
% format check on HotCRP :-(
%\titlebanner{Under submission to SOSP 2017 - do not cite or distribute}
%\preprintfooter{Draft of {\currenttime}, \today{}}

% No date in title area.
\date{}

% Paper number and no. of pages as author
\authorinfo{Paper \textbf{\#XX}}{NN pages}

\begin{document}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Cyclone: Warp Speed Replication for Key Value Stores}

@@

\begin{abstract}
The introduction of non-volatile directly attached memory in datacenters - in
the form of NVDIMMs and new memory technologies allows efficient data structures
to be built on non-volatile heaps that provide good performance coupled with
durability. However high availability remains a problem for these primarily
single machine solutions. While transactional interfaces built over RDMA capable
networking hardware offer a viable alternative, such hardware is often
unavailable in datacenters. Cyclone offers a solution to this problem by
providing transparent replication middleware that can be used with Intel's Non
Volatile Memory Library (NVML) to construct durable data-structures that map
keys to values.  Cyclone is designed around an optimized userspace networking
stack to reduce latency. Further, it can scale its consensus protocol across
cores and network ports to provide good throughput under load. We show that
Cyclone can replicate as many as 7 million updates a second using just 8 cores
(for the consensus protocol) and 4 commodity 10 GigE ports on each replica.
\end{abstract}

@@

\section{Conclusion}
Cyclone allows developers to add availability to key value maps built on top of
libraries such as NVML and achieve good performance on commodity networking
hardware. A key question is whether Cyclone can be used for other applications
such as filesystems? \emph{We believe that the requirement for scaling across
  multiple replication quorums can be satisfied by applications where the
  scalable commutativity rule~\cite{scalable_commutativity} applies to common
  case primitives.} Although our intitial release of Cyclone will be for key
value style applications, our on-going research is based on the scalable
commutativity hypothesis.
\newcommand\myurl[2]{\url{#1}}
\bibliographystyle{plainnat}
\bibliography{paper}
